% messing around with the book class

\documentclass[fontsize=11pt,paper=a5,pagesize=auto]{scrbook}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}
\usepackage[inner=1.5cm,outer=3cm,top=2cm,bottom=4cm,bindingoffset=5mm]{geometry}
\frenchspacing
\setlength{\parindent}{0.35in}

\begin{document}
\begin{titlepage}
    \vspace*{1cm}
    {\Huge\center I am Lucifer\par}
    %\noindent\hrulefill\par
    {\LARGE\center Makaria\par}
    \vfill
    {\Large\center Who Are You?\par}
\end{titlepage}
\tableofcontents

\part{Outline}
\chapter{Prologue}
\section{Life in Heaven}

Quiet, cold, and calm. Not once, not ever was there even the whisper of chaos. Not once, not ever, the rumour of unrest, disorder, or madness; and not once, not ever, was there even the smallest hint of pain or turmoil or heartache.\par
I thought nothing of it for years. It was my existence; a fact of my life, nothing more. All I knew was quiet and cold and calm. I knew nothing of pain, or of madness, or of misery, but I knew nothing also of love, or of joy, or of content. Though my very existence was light, though it was all I ever knew, I knew no warmth nor comfort. All I knew was how to \textit{be}. \par
Be quiet.

Be cold.

Be calm.
\section{The Saviour}
He was so, \textit{so} very bright.\par
I knew light. It was my name, my soul, my heart all at the same time, and wherever I dared fly or walk, light followed. From my hair to my clothes to the bright light of my eyes, always open to the world, never shut and never hidden, no one ever dared doubt my brilliance. But even I had to turn my eyes away.\par
There was all too much light to be found in him. \par
It didn't look like it, not at first. He was nothing like me; my light was marked onto near every bit of my body, and even my skin, dark and deep and almost black, shone with specks of silver stardust and golden sunshine. His face, however, was a warm, nutty brown. Yes, deep and bold like the bark of trees, but far too smooth and far too sweet to ever be mistaken for such. His hair was a similar colour, only barely darker, and his eyes, I knew nothing of. They were shut, \textit{always} shut, never for anyone to see. \par
I never dared wonder why.\par
Not when he stood before all of Heaven, tall and broad and with his face set so heavily and his lips drawn into a tight, straight line. He stood straight, also, his clothes so pure and so white and so spotless he didn't look real. And atop his head, so small but so difficult to miss for its radiance and utter power, rested a golden circlet that shone with so much brilliance I thought it would drown out the sun, and so much heat I thought I would burn no matter how far I flew.\par
And even as light flowed through me as if it were my life, I had to turn away lest I be blinded.\par 
The Prince of Heaven.\par 
The Saviour of all Mankind. \par
His light was like nothing I had ever seen. It was dangerous, it was burning, and it made me feel like there was poison filling my lungs.\par
I never once thought that that poison was ever the stronger for him.
\end{document}
